Semantic High-definition Image Synthesis \\ with a Hierarchically-nested Adversarial Network

### 2017-10-30 cvpr2018.tex
8th

%%%%%%%%% ABSTRACT
\begin{abstract}
This paper presents a novel  and effective approach to deal with the challenging task of generating synthetic photographic image conditioned on semantic image descriptions. Our method leverages the deep representations of convolutional layers and introduces hierarchical-nested adversarial training to regularize the representations to be compositional of multi-scale images. We present a new network architecture, which is intuitive as well as extensile, to push generated images to high resolutions with symmetric convolutional blocks.  We present a functional generative adversarial networks (GANs) training strategy to encourage more effective multimodal (i.e. image and text) information utilization in order to enhance multi-purpose adversary between real and fake distribution. To our best knowledge, our method is the first to show a fully end-to-end trainable network that can generate $256{\times}256$ images and is stackable to $512{\times}512$ resolution. With extensive experimental validation on three major datasets, our method significantly improves previous method and sets up a new state of the art to this field.

@@

Generative adversarial networks (GANs) have become the main solution to this task. 
Reed \etal \cite{reed2016generative} address this task through a GAN based framework. But this method only handles image up to $64{\times}64$ resolution and usually can barely generate vivid object details.
Based on \cite{reed2016generative}, Zhang \etal \cite{han2017stackgan} present a successful approach (StackGAN) by stacking another GAN to generate high-quality $256{\times}256$ images given low resolution $64{\times}64$ synthetic images. This method needs two-stage training to achieve the goal. Later on, Dong \etal \cite{dong2017semantic} 
bypasses the difficult of translate vector embedding to RGB images and treat it as an pixel-to-pixel translation \cite{isola2016image}, by re-rendering an arbitrary-style training ($128{\times}128$) image conditioned on a targeting semantic description. Unfortunately, its high resolution synthesis ability is still unclear. 
At present, how to train from the low-dimensional embedding to synthesize high resolution (e.g. $256{\times}256$) and diverse images in an end-to-end manner is still an open and attractive question.

We outline several empirical observations for this challenges using GANs, particularly for text-to-image synthesis. The first comes from a fundamental difficulty of balancing the convergence between generators and discriminators. There are a rich number of literature tacking this issue \cite{salimans2016improved,huang2016stacked}. For text-to-image synthesis, how to utilize the multimodal information between images and text in discriminator is extremely important to generate effective gradients and needs careful consideration. The second is that huge pixel space in high resolution images \cite{han2017stackgan}. 
An effective regularization to reduce the variances in generators is critical \cite{huang2016stacked}. 
Moreover, keeping semantic consistency and diversity in generated images needs more specialized designs in generators to better make use of gradients from discriminators.

%The first reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}. 
% Keeping semantic consistency as well as diversity
%The first reason comes from the fundamental difficulty of balancing the stability between generators and discriminators. There are a rich number of literature trying to stabilize GAN training \cite{salimans2016improved} and regularize networks \cite{huang2016stacked}. 
%But especially for text-to-image synthesis, how to utilize the multimodal information between images and text in discriminator is extremely important and needs careful consideration. The second reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}. Keeping semantic consistency as well as diversity in generated images needs more specialized designs for discriminators to generate effective gradients, as well as generators to prevent gradient vanishing.

With careful consideration of these outlined problems, in this paper, we propose a novel method that can directly generate high resolution and semantic consistent images trained in a fully end-to-end manner. The contributions are described follows.

To tackle the problem of space leap from text and images, our method leverages the hierarchical representations of convolutional layers through a deeply-nested layer constraint, which is simply motivated by two intuitions. 
We hope feature maps in different layers are disentangled RGB image space, which can linearly represent targeting images at corresponding resolutions and maximize the implicit effectiveness of feature representations.
We introduce accompanying hierarchically-nested adversarial objective at intermediate layers to achieve this goal. To better cooperate with discriminators, we present an quite intuitive network structure design to encourage more efficient and effective training.

To tackle the instable training of GANs, 
\textcolor{red}{we propose to enforce discriminators at different resolutions can differentiate real/fake image, correct/incorrect image-text pairs, and real/fake image pairs jointly with multiple losses.} We will show that this multi-purpose conditional strategy is mutually beneficial to encourage them only focus on respect duties. It is a regularization to limit the discriminators to use unexpected information to make decision.

@@

To synthesize high resolution image, cascade networks play an important role to decompose original difficult tasks to multiple subtasks.
Denton \etal \cite{denton2015deep} trains a cascade of GANs within a Laplacian pyramid framework (LAPGAN) and use each to generate difference images, conditioned on random noises and output from last level of the pyramid, to push up output resolution through by-stage refinement. StackGAN also shares similar strategy with LAPGAN. Following this strategy, Chen \etal \cite{chen2017photographic} present a cascaded refinement networks to synthesis high-resolution scene from semantic maps. 
Huang \etal \cite{huang2016stacked}
shows a top-down stack GAN to leverage mid-level representations, which shares some similarities with StackGAN and our method. However, this method need multiple symmetric  bottom-up discriminators and pre-training of discriminators, and the usage for high-resolution image is unclear \cite{han2017stackgan}. Compared with these strategies that train low- to high-resolution GANs progressively, our method has advantages of utilizing multi-level representations to encourage implicit subtask integration, which enables end-to-end high resolution image synthesis.

@@

@@

\textbf{zizhao's new evaluation methods.}

@@

\begin{figure}[t]
	\centering
	%	\includegraphics[width=0.48\textwidth]{}
	\caption{Results on CUB} \label{fig:vis-cub}
\end{figure}
\begin{figure}[t]
	\centering
	%	\includegraphics[width=0.48\textwidth]{}
	\caption{Results on Oxford} \label{fig:vis-oxford}
\end{figure}

%
\subsection{Comparative Results}
We compare our results with GAN-INT-CLS \cite{reed2016generative}, GAWWN \cite{reed2016learning}, TAC-GAN \cite{dash2017tac}, and StackGAN \cite{han2017stackgan} and also its improved version StackGAN++\footnote{This comes from a recently released pre-print from the author of StackGAN we just noticed, which outperforms StackGAN. Similarly with our HDGAN, it now can train $64{-}256$ directly. Each generator still take images from the bottom generator and supervised by a discriminator. Differently, our network is more like a simple Vanilla network (or a pure inverse ImageNet CNN).}.

@@

\begin{table}[t] % retrieval
	\begin{center}
		\begin{tabularx}{.268\textwidth}{ccc|c}
			\specialrule{1.5pt}{0pt}{0pt}  
			\multicolumn{3}{c|}{Components}	&  \multirow{2}{*}{Score}	\\ \cline{1-3}
				 64	& 128	& 256 			& 		\\ \hline
					&  		&	\checkmark	&	${3.52{\pm}.04}$	\\ 
						&  	\checkmark	&	\checkmark	&		\\
				\checkmark	&  			&	\checkmark	&  ${4.14{\pm}.03}$		\\
				\checkmark	&  \checkmark		&	\checkmark	&	${4.01{\pm}.04}$ \\

@@

BN is known to be problematic for ....

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
This paper presents a novel and effective approach to deal with the challenging task of generating synthetic photographic image conditioned on semantic image descriptions. We show a fully end-to-end trainable network that can generate up to $512^2$ resolution.
Our method leverages the deep representations of convolutional layers and introduces hierarchical-nested adversarial training to regularize the representations to be compositional of multi-scale images. We present a new network architecture, which is intuitive as well as extensile, to push generated images to high resolutions with symmetric convolutional blocks. We present a functional generative adversarial networks (GANs) training strategy to encourage more effective multimodal (i.e. image and text) information utilization in order to enhance multi-purpose adversary between real and fake distribution. 
With extensive experimental validation on three major datasets, our method significantly improves previous state of the arts.

@@

Generative adversarial networks (GANs) have become the main solution to this task. 
Reed \etal \cite{reed2016generative} address this task through a GAN based framework. But this method only handles image up to $64{\times}64$ resolution and usually can barely generate vivid object details.
Based on \cite{reed2016generative}, Zhang \etal \cite{han2017stackgan} present a successful approach (StackGAN) by stacking another GAN to generate high-quality $256{\times}256$ images given low resolution $64{\times}64$ synthetic images. This method needs two-stage training to achieve the goal. Later on, Dong \etal \cite{dong2017semantic} 
bypasses the difficult of translate vector embedding to RGB images and treat it as an pixel-to-pixel translation \cite{isola2016image}, by re-rendering an arbitrary-style training ($128{\times}128$) image conditioned on a targeting semantic description. Unfortunately, its high resolution synthesis ability is still unclear. 
At present, how to train from the low-dimensional embedding to synthesize high resolution (e.g. $256^2$) and diverse images in an end-to-end manner is still an open and attractive question.

We outline several empirical observations for this challenges using GANs, particularly for text-to-image synthesis. The first comes from a fundamental difficulty of balancing the convergence between generators and discriminators \cite{goodfellow2014generative,improvedGAN}. How to utilize the multimodal information between images and text in discriminator is extremely important to generate effective gradients. The second is that huge pixel space in high resolution images \cite{han2017stackgan}. 
An effective regularization to reduce the variances in generators is critical \cite{huang2016stacked}. 
Moreover, keeping semantic consistency and diversity in generated images needs more specialized designs in generators to better make use of gradients from discriminators. 
%The first reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}. 
% Keeping semantic consistency as well as diversity
%The first reason comes from the fundamental difficulty of balancing the stability between generators and discriminators. There are a rich number of literature trying to stabilize GAN training \cite{salimans2016improved} and regularize networks \cite{huang2016stacked}. 
%But especially for text-to-image synthesis, how to utilize the multimodal information between images and text in discriminator is extremely important and needs careful consideration. The second reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}. Keeping semantic consistency as well as diversity in generated images needs more specialized designs for discriminators to generate effective gradients, as well as generators to prevent gradient vanishing. 
With careful consideration of these outlined problems, in this paper, we propose a novel method that can directly generate high resolution and semantic consistent images trained in a fully end-to-end manner. The contributions are described follows.

To tackle the problem of space leap from text and images, our method leverages the hierarchical representations of convolutional layers through a deeply-nested layer constraint, which is motivated by two insights. 
First,

First, we expect feature maps at different layers are disentangled RGB image space, which can linearly represent targeting images at corresponding resolutions. And second, we maximize the implicit effectiveness of feature representations with additional supervision.
We introduce ``accompanying'' hierarchically-nested adversarial objective at intermediate layers to encourage a more effective generators. 
To better cooperate with discriminators, we present an network structure design than can uses gradient more effectively.

To better use image and text information in GAN training, 
\textcolor{red}{we enforce discriminators at different resolutions can simultaneously differentiate real and fake image-text pairs, images, and patches.}
This multi-purpose conditional strategy is mutually beneficial to encourage them only focus on respect duties. It is a regularization to limit the discriminators to use unexpected information to make decision.

@@

To synthesize high resolution image, cascade networks play an important role to decompose original difficult tasks to multiple subtasks.
Denton \etal \cite{denton2015deep} trains a cascade of GANs within a Laplacian pyramid framework (LAPGAN) and use each to generate difference images, conditioned on random noises and output from last level of the pyramid, to push up output resolution through by-stage refinement. StackGAN also shares similar strategy with LAPGAN. Following this strategy, Chen \etal \cite{chen2017photographic} present a cascaded refinement networks to synthesis high-resolution scene from semantic maps. 
Huang \etal \cite{huang2016stacked}
shows a top-down stack GAN to leverage mid-level representations, which shares some similarities with StackGAN and our method. However, this method need multiple symmetric  bottom-up discriminators and pre-training of discriminators, and the usage for high-resolution image is unclear \cite{han2017stackgan}. Karras \cite{} train progressive GAN to scale up to high resolution. Compared with these strategies that train low- to high-resolution GANs progressively, our method has advantages of utilizing multi-level representations to encourage implicit subtask integration, which enables end-to-end high resolution image synthesis.

@@

To generate $512^2$ images, we pre-train the generator to $256^2$ (and fix it for memory saving and faster convergence). We use $3$-repeat res-block followed by the stretching and linear compression layer. Since the $256^2$ image already decides the overall semantics and details, to encourage the $512^2$ maintain these information, we also use a reconstruction loss to self-regularize the generator in case the discriminator confuses the expected output.

@@

We also adopt the multi-scale structural similarity (MS-SSIM) metric \cite{improvedGAN} for further validation. It tests the variation of generated outputs and can find mode collapses reliably \cite{odena2016conditional}. Lower score indicates higher variance.

@@

\begin{figure}[t]
	\centering
	%	\includegraphics[width=0.48\textwidth]{}
	\caption{Results on CUB} \label{fig:vis-cub}
\end{figure}
\begin{figure}[t]
	\centering
	%	\includegraphics[width=0.48\textwidth]{}
	\caption{Results on Oxford} \label{fig:vis-oxford}
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width=0.4\textwidth]{figure/ms_ssmi.pdf}
	\caption{Class-wise MS-SSMI evaluation compared to StackGAN.  Note that lower score indicates higher inter-class invariance. The points below the equality line represent classes our HDGAN wins. } \label{fig:msssmi}
\end{figure}
%
\subsection{Comparative Results}
We compare our results with GAN-INT-CLS \cite{reed2016generative}, GAWWN \cite{reed2016learning}, TAC-GAN \cite{dash2017tac}, and StackGAN \cite{han2017stackgan} and also its improved version StackGAN++\footnote{This comes from a recently released pre-print from the author of StackGAN we just noticed, which outperforms StackGAN. Similarly with our HDGAN, it now can train $64{-}256$ directly. Each generator still take images from the bottom generator and supervised by a discriminator. Differently, our network is more like a simple Vanilla network (or a pure inverse ImageNet CNN).}.

@@

\begin{table}[t] % retrieval
	\begin{center}
		\begin{tabularx}{.268\textwidth}{ccc|c}
			\specialrule{1.5pt}{0pt}{0pt}  
			\multicolumn{3}{c|}{Components}	&  \multirow{2}{*}{Score}	\\ \cline{1-3}
				 64	& 128	& 256 			& 		\\ \hline
					&  		&	\checkmark	&	${3.52{\pm}.04}$	\\ 
						&  	\checkmark	&	\checkmark	&	${3.99{\pm}.04}$	\\
				\checkmark	&  			&	\checkmark	&  ${4.14{\pm}.03}$		\\
				\checkmark	&  \checkmark		&	\checkmark	&	${4.01{\pm}.04}$ \\

@@

\textbf{Advantages}
The advantages of our hierarchical-nested adversary are clearer from different views, compared with the popular stacking GAN strategy \cite{}.

First, it is memory efficient. 
When viewing it as ensembled multi-scale GAN (Figure \ref{}), each GAN fully uses the parameters of its lower resolution GAN. Usually, a deeper generator is necessary to compact a discriminator. Since the depth of discriminator increases as image resolution increases, if stacking separate GANs based on low resolution GAN outputs, much more layers are needed in generators as wells. While in our method, for instance, from a $64^2$ GAN to a $128^2$ GAN, only a minimum two conv layers ($1$-repeat res-blocks) are needed.

Second, it fully enjoys top-down knowledge. 
The low resolution can not use high resolution information in the stacking GAN strategy. While in our method, it is easy to see the low resolution GAN enjoys knowledge from higher resolution. As an evidence, our $64^2$ synthetic images have higher inception score than $64^2$ and even $128^2$ images of StackGAN (see Section 5).
